crop

### 2023-05-09 scripts/crop2boundary.Rmd
format for subset tiles for vrts

@@

tile_cells <- st_make_grid(
  bound,
  what = "polygons", square = T, flat_topped = F, crs = 4326,
  n = c(
  abs(round( (bb_vals[2] - bb_vals[1]) / 5, 0)), # rows
    abs(round( (bb_vals[3] - bb_vals[4]) / 5, 0))) #cols
) %>% 
  st_as_sf() %>% 
  rename(geometry = x) %>% 
  mutate(x = st_coordinates(st_centroid(tile_cells))[,1],
         y = st_coordinates(st_centroid(tile_cells))[,2], 
         .before = geometry, 
         across(c('x', 'y'), round, 1),
         cellname = paste0('n', abs(y), 'w', abs(x))
         )

tile_cells

@@

```{r import data which defines extent of analysis}

geom_p <- '../geodata/geomorphons/'
geo_f <- paste0(geom_p, list.files(path = geom_p, recursive = T))

geomorphons <- vrt(geo_f)
w_illi <- ext(c(-125, -85, 30, 50))

geomorphons <- crop(geomorphons, w_illi)
plot(geomorphons)

makeTiles()

(125-85) / 5 # 8 tiles x
(50-30) / 5 # 4 tiles y

>>>>

Many of these datasets are very large we are going to crop them to the area of analysis, and save the subsets.

@@

tile_cells <- st_make_grid(
  bound,
  what = "polygons", square = T, flat_topped = F, crs = 4326,
  n = c(
  abs(round( (bb_vals[2] - bb_vals[1]) / 5, 0)), # rows
    abs(round( (bb_vals[3] - bb_vals[4]) / 5, 0))) #cols
) %>% 
  st_as_sf() %>% 
  rename(geometry = x) %>% 
  mutate(x = st_coordinates(st_centroid(.))[,1],
         y = st_coordinates(st_centroid(.))[,2], 
         .before = geometry, 
         across(c('x', 'y'), round, 1),
         cellname = paste0('n', abs(y), 'w', abs(x))
         )

object.size(tile_cells)

@@

```{r geomorphons}

tile_cellsV <- vect(tile_cells)

geom_p <- '../geodata_raw/geomorphons/'
geo_f <- paste0(geom_p, list.files(path = geom_p, recursive = T))

geomorphons <- vrt(geo_f)
geomorphons <- crop(geomorphons, st_union(tile_cells))

fname <- paste0('../geodata/geomorphons/', tile_cells$cellname, "_.tif")
makeTiles(geomorphons, tile_cellsV,filename = fname, na.rm = F)

rm(geomorphons)
```
